Case Study (McKenna)

### 2020-06-03 Code/mrp/Case Study (McKenna) .Rmd
knitting to markdown
commit for example
Initial clean-up

---
title: "Case Study (McKenna)"
author: "McKenna Weech"
date: "3/10/2020"
output: html_document
---

## Intro 
Multi-level regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample. Using population knowlege sample are classified into cells baised off of choosen classification variables. Heirarchical bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevelance within the total population.

## Data 
Categorical classification variables are choosen and cell are assigned baised off of category classification. For example, if one variable is gender consisting of two categories (male and other) and one varibale is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.

In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state. Each variable is tranforemed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).

Data is generated using a function from...(find referance)

@@

options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed
```

```{r, eval = FALSE, echo = FALSE}
# Data generating function for referance. 
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

@@

# Import data. 
sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here::here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))

>>>>

---
title: "Case Study (McKenna)"
author: "McKenna Weech"
date: "3/10/2020"
output: github_document
---

Multi-level regression and post-stratification helps to infer treatment size for a whole population from a non-representative sample. Using population knowledge sample are classified into cells based off of chosen classification variables. Hierarchical Bayesian models are used to infer(?) treatment within cells and population knowlege is used to weight each cell according to their prevalence within the total population.

## Data

Categorical classification variables are chosen and cell are assigned baised off of category classification. For example, if one variable is gender consisting of two categories (male and other) and one variable is age consisting of two categories (0-50 and 50-100) then there would be four cells: male 0-50, male 50-100, other 0-50, and other 50-100.

In this case study there are five classification variables choosen: age, income, ethnicity, gender, and state. Each variable is transformed into categorical variables with age having seven categories, income having three, ethnicity having three, gender having two, and state have 50 making the total number of cells 6,300  (7 x 3 x 3 x 2 x 50 = 6300).

Data is generated using a function from...(find reference).

@@

options(mc.cores = parallel::detectCores()) # Set Stan to use all availible cores
rstan_options(auto_write = TRUE) # Don't recompile Stan code that hasn't changed

# Data generating function for referance. 
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

@@

# Importing the data. 
sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here::here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))
